Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-16 patient-clinician-workshop/pccworkshop.tex

>>>>

To this challenge we present our own personal data platform ``WebBox \cite{webbox}.'' We have used WebBox with EHRs
to enable patient collected data to be augmented with hospital-provided EHR data. WebBox is able to combine
data from multiple sources, and enables patients to make their own annotations against data, and
to optionally share these annotations, along with their activity diaries, with their clinician. This
then enables clinicians and patients to enter into a dialog about how well the patient is doing,
and any lifestyle changes they can make to better their situation.
